---
title: "Using pfsmi for BICR PFS Multiple Imputation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using pfsmi for BICR PFS Multiple Imputation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

## Overview

This vignette illustrates an end-to-end analysis of PFS assessed by BICR when local investigator PD can stop subsequent central review assessments and therefore may induce informative censoring in the BICR analysis.

```{r setup}
library(pfsmi)
```

## Simulate a hypothetical BICR trial

```{r simulate}
set.seed(2026)
dat <- simulate_bicr_data(
  n_per_arm = 100,
  med_inv = c(trt = 28, ctl = 19),
  med_bicr = c(trt = 30, ctl = 23),
  rho = 0.8,
  cutoff = 100,
  visit_interval = 6,
  disagreement = c(trt = 0.6, ctl = 0.3),
  stay = c(trt = 0.3, ctl = 0.3)
)
head(dat)
```

## Primary BICR analysis

```{r primary}
primary <- fit_pfs(dat)
primary$cox
primary$median
```

## Identify potentially informative censoring

```{r identify}
inf <- identify_informative(dat, visit_interval = 6)
table(Informative = inf, Arm = dat$trt)
```

## Run BICR multiple imputation

```{r mi}
mi <- mi_bicr(dat, m = 10, visit_interval = 6, seed = 99)
mi$cox
mi$median
```

In production analyses, use a larger number of imputations, inspect donor set sizes, and pre-specify any matching tolerances.

## Next-visit sensitivity analysis

```{r sensitivity}
sens <- sensitivity_next_visit(dat, visit_interval = 6)
sens_fit <- fit_pfs(sens, time = "pfs_sensitivity", event = "event_sensitivity")
sens_fit$cox
```

## IPCW comparator

```{r ipcw}
ipcw <- ipcw_cox(dat, censor_covariates = "trt")
summary(ipcw$fit)
summary(ipcw$weights)
```

## Interpretation

The primary analysis estimates the treatment effect under the usual non-informative censoring assumption. The next-visit sensitivity analysis represents a conservative local-PD-as-near-event assumption. The multiple imputation analysis uses arm-specific donor risk sets and continued-scan information, when available, to recover plausible BICR event times for subjects who would otherwise be censored because of local-central discrepancies.
